Proof nets for first-order additive linear logic

### 2018-08-07 ALL1.tex
subtle

	\item[Exact coverage]
The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule. Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ that are free in $C$ and $D$. For a subformula $C$ of $A$, let the \defn{free existential variables} of $C$ in $A$ be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$. A link $\link CD$ on $\seq AB$ then has \defn{exact coverage} if $\dom\sigma = \ex[A]C\cup\ex[B]D$. If it does, $\sigma$ consists of two components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we abbreviate as $\sigma_C$ and $\sigma_D$ respectively. A witness linking or pre-net has \defn{exact coverage} if all its links do.
\end{description}

>>>>

	\item[Exact coverage]
The local witness substitution $[t/x]$ in a rule instance $\qrr?t$ will have been applied exactly to the axioms $\seq a{\dual a}$ in the subproof of that rule. Correspondingly, for a link $\link CD$ on $\seq AB$ we expect the domain of $\sigma$ to be exactly the existential variables in $A$ and $B$ that (could) occur free in $C$ and $D$. For a subformula $C$ of $A$, let the \defn{free existential variables} of $C$ in $A$ be the set $\ex[A]C = \{\,x \mid C < \exists x.X \sub A\,\}$. A link $\link CD$ on $\seq AB$ then has \defn{exact coverage} if $\dom\sigma = \ex[A]C\cup\ex[B]D$. If it does, $\sigma$ consists of two components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we abbreviate as $\sigma_C$ and $\sigma_D$ respectively. A witness linking or pre-net has \defn{exact coverage} if all its links do.
\end{description}
